The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-10 Writeup/paper_v3.tex
New para on shifted binning added

>>>>

\arun{New:}To test the possibility that our choice of bins starting at $z=0.3$ with $\Delta z = 0.05$ is particularly unlucky in enhancing the effects we see, 
we carried out the same analysis using bins of the same width but shifted by $\Delta z/2$. We recomputed the overdensities keeping the parameters of the redshift distributions same as before.
Shifting the bins enhances the overdensities and underdensities in some cases and in other cases, it mixes the overdense and underdense regions to make it more neutral-like. 
The environmental trends are observed in the enhanced bins and hence our conclusions are still applicable.
